Replicability across populations (S7.2)

### 2024-03-04 manuscript/supp-figure3.tex
Manuscript revision 2

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\der}{\text{d}}
\newcommand{\e}{\text{e}}
\newcommand{\Ne}{N_{\text{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\text{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S_{0}}
\newcommand{\SphyDel}{\mathcal{D}_0}
\newcommand{\SphyNeu}{\mathcal{N}_0}
\newcommand{\SphyBen}{\mathcal{B}_0}
\newcommand{\Sphyclass}{x}
\newcommand{\SphyclassAlt}{y}
\newcommand{\given}{\mid}
\newcommand{\Spop}{S}
\newcommand{\SpopDel}{\mathcal{D}}
\newcommand{\SpopNeu}{\mathcal{N}}
\newcommand{\SpopBen}{\mathcal{B}}
\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
\newcommand{\AdvMean}{\beta_b}
\newcommand{\DelMean}{\beta_d}
\newcommand{\thetaSyn}{\theta_{\text{S}}}

\title{Replicability of figure 3 across populations}
\date{~}
\author{~}

\begin{document}
    \maketitle
    \tableofcontents

    \newpage

    (Top-left) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
    Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)

    (Top-right) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the tree.
    If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.

    (Bottom-left) The site-frequency spectrum (SFS) for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
    The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
    At high frequencies, deleterious mutations are underrepresented.

    (Bottom-right) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
    Proportions depicted here are not weighted by their mutational opportunities.
    \section{Bos taurus}

@@

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Bos_taurus.IRBT.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Uganda}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Bos_taurus.UGBT.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Capra}

@@

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.AUCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{France}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.FRCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Iran (C. aegagrus)}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCA.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Iran}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Italy}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.ITCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Morocco}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.MOCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Chlorocebus sabaeus}

@@

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Barbados.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Central Afr. Rep.}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Central_African_Republic.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Ethiopia}

>>>>

\title{Replicability across populations (S7.2)}
\date{~}
\author{~}

\begin{document}
    \maketitle
    \tableofcontents
    \newpage

    \section{Bos taurus}

@@

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Bos_taurus.IRBT.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Bos_taurus.IRBT.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{Uganda}

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Bos_taurus.UGBT.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Bos_taurus.UGBT.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \section{Capra}

@@

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.AUCH.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.AUCH.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{France}

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.FRCH.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.FRCH.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{Iran (C. aegagrus)}

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.IRCA.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.IRCA.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{Iran}

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.IRCH.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.IRCH.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{Italy}

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.ITCH.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.ITCH.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{Morocco}

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.MOCH.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.MOCH.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \section{Chlorocebus sabaeus}

@@

    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny A: Expected DFE for mutations}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny B: Expected DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.Flow.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny C: Observed DFE for substitutions}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Barbados.bins3Mask0.9.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny D: Observed DFE for polymorphisms}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Barbados.bins3Mask0.9.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny E: Site frequency spectrum}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \subsection{Central Afr. Rep.}
